\ttitle

### 2013-02-04 Chapters/Chapter2.tex
Worked on HMM

>>>>

Generally a HMM can be fully connected, or ergodic model. Other configurations 
are also possible, of which the left-right model, or Bakis model, is popular 
for temporal applications \cite{rabiner1989tutorial}. This because the 
structure of the state probability distribution resembles the construction of 
possible states over time. This left-right model can be generalized by setting
\begin{eqnarray}
a_{ij} = 0, & j > i + \Delta
\end{eqnarray}
for some $\Delta$, indicating the possible \emph{distance} of the jumps over 
states.

*** [INSERT GRAPHICS SHOWING STRUCTURE OF HMM]

In \cite{oliver2002layered} it is stated that HMMs are robust mechanisms with 
respect to changes in temporal segmentation of observations, although they 
suffer from a few problems when applied to reason about longer and complexer 
sequences over time. They state that, especially with limited training data, 
the HMM tend to be overfitted and tend to lack structure and have an excess of 
parameters. The overcome this limitation, they introduce a Layered Hidden 
Markov Model (LHHM) which they show is more robust to temporal changes in 
observations. They make use of the hypothesis from the field of psychology, 
that human behavior is hierarchically structured \cite{zacks2001event}.
